AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-02 publications/dora_outlier_detection_iaai.tex
Add description of rover target data set and relevant updates to acknowledgements (#42)

@@

\subsection{DORA configurable pipeline} Steven please add details about the 
approach/design choices for this pipeline. Mention that additional data types, 
feature extraction methods, ranking algorithms, and results organization and 
visualization modules can easily be added and integrated if they follow the API. 
Hannah to add architecture figure. Add descriptions of each layer of modules: 
\paragraph{Data types} Hannah
\paragraph{Feature extraction} Hannah 
\paragraph{Ranking algorithms} We implemented 7 algorithms for scoring and 
ranking samples by outlierness. [Describe each algorithm briefly and how they 
complement each other.]

@@

\subsubsection{Targets in Mars rover images}
Kiri

@@

\subsubsection{Targets in Mars rover images}
Kiri

@@

\section{ Acknowledgments}
Funding/support: JPL CIF, SMD etc. Acknowledge people who contributed to 
datasets e.g. FAO, Matt Pritchard, DES, other CIF team members?

>>>>

\usepackage{siunitx}
\usepackage[dvipsnames]{xcolor}
\newcommand{\todo}[1]{\textcolor{blue}{#1}}

@@

\subsection{DORA configurable pipeline} Steven please add details about the 
approach/design choices for this pipeline. Mention that additional data types, 
feature extraction methods, ranking algorithms, and results organization and 
visualization modules can easily be added and integrated if they follow the API. 
Hannah to add architecture figure. Add descriptions of each layer of modules: 
\paragraph{Data types} Hannah
\paragraph{Feature extraction} Hannah 
\paragraph{Ranking algorithms.} We implemented 7 algorithms for scoring and 
ranking samples by outlierness. [Describe each algorithm briefly and how they 
complement each other.]

@@

\subsubsection{Targets in Mars rover images.}
Mars exploration is fundamentally an exercise in discovery with the
goal of increasing our understanding of the history, evolution,
composition, and currently active processes on Mars.  Outliers
identified in Mars observations can inspire new discoveries and inform
the choice of which areas merit follow-up, deeper
investigation~\cite{kerner2020comparison,wagstaff:rover-novelty20}.
We collected \todo{XXX} images from the Mars Science Laboratory's
Navigation camera (Navcam) and employed the Rockster~\cite{burl:rockster16}
method used by onboard rover software to identify candidate rock
targets with an area of at least 100 pixels, yielding \num{6005}
targets.  We cropped out a \num{64}$\times$\num{64} pixel image
centered on each target.
%
We collaborated with an MSL science planning team member to
independently review the targets and identify those that were
considered novel by the mission ($n_{novel} = 108$).

@@

\subsubsection{Targets in Mars rover images.}
Kiri
% and organized them chronologically.
\subsubsection{Satellite time series for ground-truth observations}
Hannah: Describe the Earth crop field data set and applications

@@

\section{Acknowledgments}
\todo{Funding/support: JPL CIF, SMD etc.}
We thank the NASA Center Innovation Fund for supporting this work.

\todo{Acknowledge people who contributed to 
datasets e.g. FAO, Matt Pritchard, DES, other CIF team members?}

We thank Raymond Francis for analyzing the Navcam rover images to
identify targets considered to be ``novel'' for evaluating outlier
detection in the planetary rover scenario.

Part of this research was carried out at the Jet Propulsion
Laboratory, California Institute of Technology, under a contract with
the National Aeronautics and Space Administration.
